---
title: "Weekly_Data_Processing"
author: "Benny Rice"
date: "2/8/2021"
output: html_document
---

```{r setup, include = FALSE, eval = TRUE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

***
***
<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

## HEADER INFO

- Benny Rice | Department of Ecology and Evolutionary Biology | Princeton University | b.rice@princeton.edu
- Code associated with processing data from the **Impacts of COVID-19 on Malagasy STEM** project
- Apologies in advance for amateurish code (ie all the loops and clunkiness)
- In collaboration with Lova Marline, Miary Raselimanana, Seheno Andriantsaralaza, Hervet Randriamady and others

</div>

***

(Set up: Loading necessary libraries)
```{r i1, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(reshape2)
library(ggpubr)
library(ggalt)
library(ggrepel)
library(here)
library(gridExtra)
library(readxl)
```

***
***

#### OUTLINE:

- **Section 1 |** Reading in data downloaded from Kobo Collect
- **Section 2 |** Cleaning data (in progress)
- **Section 3 |** Progress summaries: Summary stats and sampling time series
- **Section 4 |** Preliminary data visualizations: Breakdown by gender
- **Section 5 |** ...



**FIX** Update outline at the end (add figures and tables interspersed ^)


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 1 | Reading in data downloaded from Kobo Collect (xls form, English)

</div>

***
***

- Data is read from an xlsx file that is manually downloaded from the Kobo Collect account
  - [KoBoToolbox](https://kf.kobotoolbox.org/#/forms) --> `Impacts of Covid-19 on Malagasy STEM` --> `DATA` --> `Downloads`
  - Selecting export options:
    - Export type `XLS`
    - Value and header format `XML values and headers`
    - `Advanced options`: Select `Include fields from all 32 deployed versions`
      - Note this will include a series of columns at the far end corresponding to changed questions
      - Note: Manually delete the `add_info` column
        - This column contains a free text response from respondents; deleted in case there is personal info within
  - Manually uploading to [the GitHub repository for this project](https://github.com/labmetcalf/COVID_STEM_MADA)
- Data file name should include the date at which data was downloaded

```{r 1.01}
k.data <- read_xlsx(here(
  "DATA/DATA_08_Impacts_of_Covid-19_on_Malagasy_STEM_-_all_versions_-_False_-_2021-05-09-10-27-09.xlsx"))
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 2 | Cleaning data (in progress)

</div>

***
***

#### Section 2.1 | Removing junk rows and junk columns

**(1)** Removing incomplete surveys or ineligible respondents

- Removing individuals who chose not to start the survey
- Removing individuals who are not Malagasy or did not live in Madagascar in 2020
- Removing individuals who are not in a STEM field

- Removing individuals with unlikely/illogical responses (e.g., age 100 years but walks to work each day)

```{r 2.01.1, echo = FALSE}
k.data <- k.data %>% 
  filter(!is.na(agreement))   %>% filter(agreement   == "yes")  %>%
  filter(!is.na(nationality)) %>% filter(nationality == "gasy") %>%
  filter(!is.na(residence))   %>% filter(residence   == "yes") %>%
  filter(!is.na(field))       %>% filter(field       != "nonstem") %>%
  filter(!is.na(gender))
```

**(2)** Removing columns that do not contain data

```{r 2.01.2, echo = FALSE}
k.data <- k.data %>% 
            #Removing intro prompt (no data)
  select(-c(`Nous_effectuons_une_ent_pour_votre_temps`,
            #Removing prompt before publications question (no data)
            `_3_09_Veuillez_indiq_proceedings_livres`,
            #Removing prompt for if HH size exceed 15 (no data) 
            `Si_plus_de_10_indivi_plus_g_s_ci_dessus`,
            #Removing GPS data (auto-collected and not accurate)
            `store_gps`, `_store_gps_latitude`, `_store_gps_longitude`, 
            `_store_gps_altitude`, `_store_gps_precision`,
            #Removing prompts thanking the respondent and finishing the survey (no data)
            `Merci_pour_votre_tem_ns_une_bonne_journ_e`, `L_ENQUETE_SE_TERMINE_VOTRE_PARTICIPATION_`,
            `Nous_vous_remercions_STEM_Madagascar`, `THIS_COMPLETES_THE_S_H_FOR_PARTICIPATING__001`,
            `We_are_conducting_a_nk_you_for_your_time`,
            #age and student status columns from a draft version that were never deployed  (no data)
            `age_a`, `age_b`, `age_c`, `display`, `student_yes_no`, `level`,
            #more draft columns  (no data)
            `_3_12_Please_list_th_e_proceedings_books`, `_3_12_Veuillez_indiq_proceedings_livres`,
            `_3_12B_Please_list_t_e_proceedings_books`, `_3_12B_Please_list_th_e_proceedings_books`,
            #columns for questions related to computer issues, question was dropped (only 7 respondents)
            `computer_issue`, `computer_issue/noissue`, `computer_issue/cantconnect`, `computer_issue/nocam`,
            `computer_issue/batissue`, `computer_issue/crashoften`, `computer_issue/lostwork`,
            `computer_issue/lackssoft`, `computer_issue/diffconnectvideo`, `computer_issue/keyboard`,
            `computer_issue/usephone`, `computer_issue/slowcomp`, `computer_issue/frustraoldcomp`,
            `computer_issue/na`,
            #columns for an abonded way of asking about age and sex of hh members (only 7 respondents)
            `sex_hh_memb`, `_4_04_Veuillez_indiq_us_EN_VOUS_EXCLUANT`, `_4_04_Please_indicat_u_NOT_INCLUDING_YOU`,
            `sex_hh_memb_001`, `_0_5`, `_5_10`, `sex_hh_memb_002`, `_10_15`, `_15_20`, `sex_hh_memb_003`, `_20_25`, 
            `_25_30`, `sex_hh_memb_004`, `_30_50`, `_50_55`, `sex_hh_memb_005`, `_55_60`, `_60_65`,
            `sex_hh_memb_006`, `_65_plus`, `If_more_than_10_indi_st_individuals_above`, 
            `sex_hh_memb_007`, `sex_hh_memb_008`, `sex_hh_memb_009`,
            #columns for dropped questions without data (no data)
            `week_inter_cov`, `week_inter_house`, `stress_house`, `stress_infectfam`,
            #columns for questions related to transpo disruptions, and illness
            #question was dropped (only 7 respondents)
            `disrup_transp`, `illness`, `stop_day_covid`,
            #Prompts for concluding the survey (no data)
            `Thank_you_for_your_t_wish_you_a_great_day`, `THIS_COMPLETES_THE_S_H_FOR_PARTICIPATING_`,
            `Thank_you_for_your_i_STEM_in_Madagascar`,
            #Unnecessary auto generated columns
            `_id`, `_uuid`, `_validation_status`, `_notes`, `_status`, `_submitted_by`, `_tags`))
```

#### Section 2.2 | Renaming problematic column names

1. columns starting with weird characters: `_index` to `index`; `_submission_time` to `submission_time`
2. columns with uninformative names: `age` to `year_of_birth`
3. `research_fund_bef`:`fund_pend`: making research funding question column names more intuitive


```{r 2.02, echo = FALSE}
k.data <- k.data %>% 
  rename(index = `_index`) %>% rename(submission_time = `_submission_time`) %>%
  rename(year_of_birth = age) %>%
  #Research funds
  rename(res_fund_amt_bef  = research_fund_bef, #Before pandemic, approx. total res funds managed
         res_fund_y_n_dur  = research_fund,     #During the pandemic, did you receive funds
         res_fund_dur_nb   = research_fund_nb,  #If yes, number of grants/funds received
         res_fund_amt_curr = research_fund_dur, #Approx. total res funds managed currently
         res_fund_issue    = fund_issue,        #Did the pandemic cause issues with accessing funds
         res_fund_app_dur  = fund_pend_yes_no,  #During the pandemic, Did you apply for funds?
         res_fund_pend_nb  = fund_pend          #If yes, how many grant applications are pending
         )
```

#### Section 2.3 | Removing individuals with unlikely/illogical responses

1. `index` = `990`: Individual sampled 2021-05-06 reported age of 100 years but walks to work each day


```{r 2.03, echo = FALSE}
k.data <- k.data %>% filter(!(today == "2021-05-06" & year_of_birth == "1921" & index == 990))
```

#### Section 2.4 | Recoding multiple choice selection options

1. `degree` : combining `master` and `maitrise` to `masters`; `license` to `bachelors`
2. `month_closed`: options for 1-2 months, 2-3 months erroneously formatting as dates; convert to characters

```{r 2.04, echo = FALSE}
k.data <- k.data %>% mutate(degree = recode(degree,
    "maitrise" = "masters",
    "master"   = "masters",
    "licence"  = "bachelors"))

#month_closed options: 0_1_mos, 1_2_mos, 2_3_mos, 3_4_mos, 4_5_mos, 5plus_mos
k.data <- k.data %>% mutate(month_closed = recode(month_closed,
    "less1"               = "0_1_mos",
    "2021-01-02 00:00:00" = "1_2_mos",
    "2021-02-03 00:00:00" = "2_3_mos",
    "2021-03-04 00:00:00" = "3_4_mos",
    "2021-04-05 00:00:00" = "4_5_mos",
    "more5"               = "5plus_mos"))
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 3 | Cleaning up "other" responses

</div>

***
***
***

Questions with "other" responses:

1. Field of study (`other_field`)
2. Academic stage / position (`other_acad`)
3. Type of institution (`other_inst`)
4. Challenges to attend online opportunities (`other_challenge_opport`)T
  
- Changing text responses by hardcoding following the tables below

***

**1. Field of study**

- Listing other responses

```{r 3.01A, echo = FALSE}
paste0("Number of unique other responses: ", length(unique(tolower(k.data$other_field))) - 1)
unique(tolower(k.data$other_field[!is.na(k.data$other_field)]))
```

##### Original options and cleaned groupings:

| code                   | full text                                   | field_cleaned                       |
| ---------------------- | ------------------------------------------- | ----------------------------------- |
| agri_natres            | Agriculture & Natural Resources             | Agriculture & Natural Resources     |
| agro                   | Agronomic Sciences                          | Agriculture & Natural Resources     |
| astro	                 | Astronomy & Astrophysics                    | Physical Sciences                   |
| atmo_earth_ocean       | Atmospheric, Earth & Ocean Sciences         | Atmospheric, Earth & Ocean Sciences |
| biochem_cell_mol_biolo | Biochemistry, Cellular & Molecular Biology  | Biological Sciences                 |
| bio_sci                | Biological Sciences                         | Biological Sciences                 |
| chem_chemeng           | Chemistry & Chemical Engineering            | Physical Sciences                   |
| clinicsci              | Clinical Sciences                           | Clinical & Health Sciences          |
| comp_scien             | Computer Science                            | Computer Science                    |
| eletc_mech             | Electrical & Mechanical Engineering         | Engineering Sciences                |
| enviro                 | Environmental Science                       | Environmental Sciences              |
| health_sci             | Health Sciences                             | Clinical & Health Sciences          |
| math_stat              | Mathematics & Statistics                    | Mathematics & Statistics            |
| pharm_cosmet           | Pharmacology, Physiology & Cosmetology      | Clinical & Health Sciences          |
| physic                 | Physics                                     | Physical Sciences                   |
| other_eng	             | Other Engineering Sciences                  | Engineering Sciences                |
| nonstem                | Non-STEM field                              | Non-STEM                            |

```{r 3.01B, echo = FALSE}
#Replacing other responses with code from original options
k.data <- k.data %>% mutate(other_field = tolower(other_field)) %>%
  mutate(other_field = recode(other_field,
    "géologie"                           = "atmo_earth_ocean",
    "hydrosciences"                      = "atmo_earth_ocean",
    "sciences agronomiques"              = "agri_natres",
    "pharmacologie"                      = "health_sci",
    "pharmacology"                       = "health_sci",
    "pharmacologie et cosmétologie"      = "health_sci",
    "nutrition"                          = "health_sci",
    "pharmarmacologie, cosmetic"         = "health_sci",
    "sciences et technique nucleaires"   = "physic",
    "sciences et techniques nucléaires"  = "physic",
    "ecotourism science"                 = "enviro",
    "paléontologie"                      = "bio_sci",
    "science et technologie"             = "comp_sci",
    "paleontology"                       = "bio_sci",
    "marine biology"                     = "bio_sci",
    "administration"                     = "nonstem",
    "marine science"                     = "atmo_earth_ocean",
    "animal health sciences"             = "bio_sci",
    "etudes envionnementales en général" = "enviro",
    "zoology"                            = "bio_sci",
    "entomologie"                        = "bio_sci",
    "physique nucléaire"                 = "physic",
    "économie de la santé"               = "health_sci",
    "géographie"                         = "atmo_earth_ocean",
    "science de la terre"                = "atmo_earth_ocean",
    "science de la nature et de l'ecosystème"                 = "enviro",
    "sciences nucleaires, physiques, nanotechnologie"         = "physic",
    "sciences techniques nucleaires et nanotechnologie"       = "physic",
    "sciences de l'environnement et du développement durable" = "enviro",
    #09 May 2021 updates
    "génie civil"                          = "other_eng",
    "hydrographie industriel et thermique" = "atmo_earth_ocean",
    "hydrologie"                           = "atmo_earth_ocean",
    "medecine humaine"                     = "clinicsci"
    ))
#Deleting 1 individual who selected other and wrote nonstem
#Removing ineligible participants (e.g., still undergraduate students)
# Keeping rows where other_acad = NA (participant selected one of the standard options)
k.data <- k.data %>% filter(is.na(other_field) | other_field != "nonstem")
```

##### Creating cleaned, standardized columns (1s and 0s for each option)

##### Cleaned codes

| code                   | code_cleaned | field_cleaned                       |
| ---------------------- | ------------ | ----------------------------------- |
| agri_natres            | agro_sci     | Agriculture & Natural Resources     |
| agro                   | agro_sci     | Agriculture & Natural Resources     |
| comp_scien             | comp_sci     | Computer Science                    |
| atmo_earth_ocean       | earth_sci    | Atmospheric, Earth & Ocean Sciences |
| eletc_mech             | engi_sci     | Engineering Sciences                |
| other_eng	             | engi_sci     | Engineering Sciences                |
| enviro                 | env_sci      | Environmental Sciences              |
| health_sci             | health_sci   | Clinical & Health Sciences          |
| pharm_cosmet           | health_sci   | Clinical & Health Sciences          |
| clinicsci              | health_sci   | Clinical & Health Sciences          |
| biochem_cell_mol_biolo | life_sci     | Biological Sciences                 |
| bio_sci                | life_sci     | Biological Sciences                 |
| math_stat              | math_stats   | Mathematics & Statistics            |
| astro	                 | phys_sci     | Physical Sciences                   |
| chem_chemeng           | phys_sci     | Physical Sciences                   |
| physic                 | phys_sci     | Physical Sciences                   |
| nonstem                | non_stem     | Non-STEM                            |

***

Criteria:

***

For each, the respondent either selected that STEM field  or selected other but their response is categorized as that field For example, for Agriculture & Natural Resources:

STEM field = Agriculture & Natural Resources `agro_sci`: 
  1. selected `agri_natres` or `agro`
  2. selected other field but other response is `agri_natres` or `agro`

***

```{r 3.01C, echo = FALSE}
k.data <- k.data %>%
  #agro_sci
  mutate(agro_sci = case_when(
    `field/agri_natres` == "1"           ~ 1,
    `field/agro`        == "1"           ~ 1,
     other_field        == "agri_natres" ~ 1,
     other_field        == "agro"        ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #comp_sci
  mutate(comp_sci = case_when(
    `field/comp_scien` == "1"          ~ 1,
     other_field       == "comp_scien" ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #earth_sci
  mutate(earth_sci = case_when(
    `field/atmo_earth_ocean` == "1"                ~ 1,
     other_field             == "atmo_earth_ocean" ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #engi_sci
  mutate(engi_sci = case_when(
    `field/eletc_mech` == "1"          ~ 1,
    `field/other_eng`  == "1"          ~ 1,
     other_field       == "eletc_mech" ~ 1,
     other_field       == "other_eng"  ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #env_sci
  mutate(env_sci = case_when(
     other_field   == "enviro" ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #health_sci
  mutate(health_sci = case_when(
    `field/health_sci`   == "1"            ~ 1,
    `field/pharm_cosmet` == "1"            ~ 1,
    `field/clinicsci`    == "1"            ~ 1,
     other_field         == "health_sci"   ~ 1,
     other_field         == "pharm_cosmet" ~ 1,
     other_field         == "clinicsci"    ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #life_sci
  mutate(life_sci = case_when(
    `field/biochem_cell_mol_biolo` == "1"                      ~ 1,
    `field/bio_sci`                == "1"                      ~ 1,
     other_field                   == "biochem_cell_mol_biolo" ~ 1,
     other_field                   == "bio_sci"                ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #math_stats
  mutate(math_stats = case_when(
    `field/math_stat` == "1"         ~ 1,
     other_field      == "math_stat" ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #phys_sci
  mutate(phys_sci = case_when(
    `field/astro`        == "1"            ~ 1,
    `field/chem_chemeng` == "1"            ~ 1,
    `field/physic`       == "1"            ~ 1,
     other_field         == "astro"        ~ 1,
     other_field         == "chem_chemeng" ~ 1,
     other_field         == "physic"       ~ 1,
     is.na(field) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #Removing old field columns
  select(start:residence, 
         agro_sci, comp_sci, earth_sci, engi_sci, env_sci, health_sci, life_sci, math_stats, phys_sci, 
         year_of_birth:index)
```


***

**2. Academic stage / position**


- Listing other responses

```{r 3.02A, echo = FALSE}
paste0("Number of unique other responses: ", length(unique(tolower(k.data$other_acad))) - 1)
unique(tolower(k.data$other_acad[!is.na(k.data$other_acad)]))
```

##### Original options and cleaned groupings:

| code                   | full text                                           | field_cleaned                |
| ---------------------- | --------------------------------------------------- | ---------------------------- |
| master_student         | Master's student                                    | Masters Student              |
| masterstud             | Master's student                                    | Masters Student              |
| phdcandidate_student   | PhD candidate or student                            | PhD Student                  |
| phd_stud               | PhD candidate or student                            | PhD Student                  |
| postgrad               | Post-graduate student                               | Postgraduate Student         |
| postdoc                | Postdoctoral researcher                             | Postdoc                      |
| research_assist        | Research assistant                                  | Research Assistant or Tech   |
| instructor             | Faculty member, Professor, or University Instructor | Faculty, PI, or Senior Level |
| consult                | Consultant                                          | STEM Professional            |
| research_officer       | Research officer                                    | STEM Professional            |
| independent_researcher | Independent researcher                              | STEM Professional            |
| retired_scientist      | Retired scientist (No longer engaged in research)   | Retired scientist            |
| NA_not_eligible        | Not eligible                                        | Not eligible                 |


```{r 3.02B, echo = FALSE}
#Replacing other responses with code from original options
k.data <- k.data %>% mutate(other_acad = tolower(other_acad)) %>%
  mutate(other_acad = recode(other_acad,
    "medicin"                              = "research_officer",
    "médecin"                              = "research_officer",
    "professeur"                           = "instructor",
    "etudiante en licence"                 = "NA_not_eligible",           #Not eligible, still an undergrad
    "directeur général"                    = "instructor",
    "président gerp"                       = "instructor",
    "fonctionnaire de l'état"              = "research_officer",
    "professeur titulaire"                 = "instructor",
    "clo multidisciplinaire"               = "research_officer",
    "formation spécialisée"                = "research_officer",
    "chercheur biologiste"                 = "research_officer",
    "travailleur"                          = "research_officer",
    "monitoring and evaluation"            = "research_officer",
    "suivi évaluation"                     = "research_officer",
    "cco  (biologiste preleveur)"          = "research_officer",
    "chef de volet conservation"           = "instructor",
    "travailleurs"                         = "research_officer",
    "thesard doctorat d'exercice"          = "phd_stud",
    "responsable technique"                = "research_officer",
    "secrétaire de direction"              = "research_officer",
    "secrétaire"                           = "research_officer",
    "technicienne de surface"              = "research_assist",
    "responsable environnement"            = "research_officer",
    "responsable ictc"                     = "research_officer",
    "en recherche de finacement"           = "research_officer",
    "recently graduate"                    = "postgrad",
    "ministre"                             = "instructor",
    "aucun"                                = "postgrad",
    "directeur du parc"                    = "instructor",
    "directeur"                            = "instructor",
    "salariée"                             = "research_officer",
    "enseignant vacataire"                 = "phd_stud",
    "responsable laborat"                  = "research_officer",
    "responsable d'hygiène"                = "research_officer",
    "enseignante vacataire"                = "phd_stud",
    "entrepreneur"                         = "research_officer",
    "technicien de production"             = "research_assist",
    "graduate"                             = "postgrad",
    "assistant d'enseignement supérieur"   = "research_assist",
    "ingénieur de maintenance"             = "research_officer",
    "cadre dans une entreprise"            = "instructor",
    "enseignant-chercher (vacataire)"      = "instructor",
    "technicien de laboratoire"            = "research_assist",
    "enseignant vacataire,   consultant"   = "research_officer",
    "chef de projet dans la conservation"  = "instructor",
    "enseignant vacataire-informaticien"   = "phd_stud",
    "coordinateur de projet"               = "research_officer",
    "chargé d'études environnementales"    = "research_officer",
    "coordinatrice de projet"              = "research_officer",
    "master ii"                            = "master_student",
    "chercheur, chef d'unité"              = "instructor",
    "practitioner in marine conservation"  = "research_officer",
    "chef service administratif et financier"     = "research_officer",
    "responsable production et environnement"     = "research_officer",
    "respo admin personnel et juridique"          = "research_officer",
    "cadre dans un projet de développement"       = "research_officer",
    "i still study at the undergraduate level"    = "NA_not_eligible",         #Not eligible, still an undergrad
    "gestionnaire de site aires protégées marine" = "research_officer",
    "gestionnaire aire protégée"                  = "research_officer",
    "coordinatrice d'étude clinique"              = "research_officer",
    "socio-organisateur dans ong blue ventures"   = "research_officer",
    "manager en éducation environnementale"       = "research_officer",
    "en cours de preparation de l'inscription au doctorat" = "postgrad",
    "administration (asity) et responsable de formation"   = "research_officer",
    "i am recently graduated and would like to wait a while before continuing my study" = "postgrad",
    #09 May 2021 updates
    "ingénieur en mécanique"             = "research_officer",
    "volontaire"                         = "postgrad",
    "biologiste"                         = "research_officer",
    "interne en médecine et thésard"     = "phd_stud",
    "chef de projet"                     = "instructor",
    "responsable conservation"           = "research_officer",
    "ingénieur informatique"             = "research_officer",
    "je n'ai pas de position académique" = "research_officer",
    "none"                               = "research_officer",
    "enseignants vacataire"              = "instructor"
    ))

#Removing ineligible participants (e.g., still undergraduate students)
# Keeping rows where other_acad = NA (participant selected one of the standard options)
k.data <- k.data %>% filter(is.na(other_acad) | other_acad != "NA_not_eligible")
```

##### Creating cleaned, standardized columns (1s and 0s for each option)

##### Cleaned codes

| code                   | code_cleaned | field_cleaned                |
| ---------------------- | -------------|----------------------------- |
| master_student         | student_ms   | Masters Student              |
| masterstud             | student_ms   | Masters Student              |
| phdcandidate_student   | student_phd  | PhD Student                  |
| pdhstud                | student_phd  | PhD Student                  |
| postgrad               | postgrad     | Postgraduate Student         |
| postdoc                | postdoc      | Postdoc                      |
| research_assist        | ra_tech      | Research Assistant or Tech   |
| instructor             | senior_pi    | Faculty, PI, or Senior level |
| consult                | staff_res    | STEM Professional            |
| research_officer       | staff_res    | STEM Professional            |
| independent_researcher | staff_res    | STEM Professional            |
| retired_scientist      | ret_sci      | Emeritus                     |
| NA_not_eligible        | NA_inelig    | Not eligible                 |

***

Criteria:

***

Academic stage or position = Masters Student `student_ms`: 

  1. selected acad stage as master (`acad/master_student` == "1" | `acad/masterstud` == "1")
  2. selected other acad stage but other response is master (`other_acad == "master_student" | other_acad == "masterstud"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad %in% c("master_student", "masterstud")`) 

***

Academic stage or position = PhD Student `student_phd`: 

  1. selected acad stage as PhD (`acad/phdcandidate_student` == "1" | `acad/pdhstud` == "1")
    - Note that PhD student code was misspelled in original survey deployment: pdh not phd
  2. selected other acad stage but other response is PhD (`other_acad == "phd_stud"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad %in% c("phdcandidate_student", "pdhstud")`) 

***

Academic stage or position = Postgraduate Student `postgrad`: 

  1. selected other acad stage but other response is postgrad (`other_acad == "postgrad"`)

***

Academic stage or position = Postdoc `postdoc`: 

  1. selected acad stage as Postdoc (`acad/postdoc` == "1")
  2. selected other acad stage but other response is postdoc (`other_acad == "postdoc"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad == "postdoc"`) 

***

Academic stage or position = Research Assistant or Tech `ra_tech`: 

  1. selected acad stage as ra_tech (`acad/research_assist` == "1")
  2. selected other acad stage but other response is ra_tech (`other_acad == "research_assist"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad == "research_assist"`) 

***

Academic stage or position = Faculty, PI, or Senior level `senior_pi`: 

  1. selected acad stage as senior_pi (`acad/instructor` == "1")
  2. selected other acad stage but other response is senior_pi (`other_acad == "instructor"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad == "instructor"`) 

***

Academic stage or position = STEM Professional `staff_res`: 

  1. selected acad stage as staff_res 
    (`acad/consult` == "1" | `acad/research_officer` == "1" | `acad/independent_researcher` == "1")
  2. selected other acad stage but other response is staff_res (`other_acad == "research_officer"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad == "consult" | acad == "research_officer" | acad == "independent_researcher"`) 

***

Academic stage or position = Emeritus `ret_sci`: 

  1. selected acad stage as ret_sci (`acad/retired_scientist` == "1")
  2. selected other acad stage but other response is staff_res (`other_acad == "retired_scientist"`)
  3. Note for some February 5 surveys, the columns with 1s and 0s for each option did not automatically generate
    - (`acad == "retired_scientist"`) 


```{r 3.02C, echo = FALSE}
k.data <- k.data %>%
  #student_ms
  mutate(student_ms = case_when(
    `acad/master_student` == "1"              ~ 1,
    `acad/masterstud`     == "1"              ~ 1,
     other_acad           == "master_student" ~ 1,
     other_acad           == "masterstud"     ~ 1,
     acad %in% c("master_student", "masterstud") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #student_phd
  mutate(student_phd = case_when(
    `acad/phdcandidate_student` == "1"        ~ 1,
    `acad/pdhstud`              == "1"        ~ 1,
     other_acad                 == "phd_stud" ~ 1,
     acad %in% c("phdcandidate_student", "pdhstud") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #postgrad
  mutate(postgrad = case_when(
     other_acad == "postgrad" ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #postdoc
  mutate(postdoc = case_when(
    `acad/postdoc` == "1"       ~ 1,
     other_acad    == "postdoc" ~ 1,
     acad %in% c("postdoc") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #ra_tech
  mutate(ra_tech = case_when(
    `acad/research_assist` == "1"               ~ 1,
     other_acad            == "research_assist" ~ 1,
     acad %in% c("research_assist") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #senior_pi
  mutate(senior_pi = case_when(
    `acad/instructor` == "1"          ~ 1,
     other_acad       == "instructor" ~ 1,
     acad %in% c("instructor") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #staff_res
  mutate(staff_res = case_when(
    `acad/consult`                == "1"                ~ 1,
    `acad/research_officer`       == "1"                ~ 1,
    `acad/independent_researcher` == "1"                ~ 1,
     other_acad                   == "research_officer" ~ 1,
     acad %in% c("consult", "research_officer", "independent_researcher") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #ret_sci
  mutate(ret_sci = case_when(
    `acad/retired_scientist` == "1"                 ~ 1,
     other_acad              == "retired_scientist" ~ 1,
     acad %in% c("retired_scientist") ~ 1,
     is.na(acad) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #Removing old academic stage columns
  select(start:degree, student_ms, student_phd, postgrad, postdoc, ra_tech, senior_pi, staff_res, ret_sci, affiliation:index)
```


***

**3. Type of institution**

##### Listing other responses

```{r 3.03A, echo = FALSE}
paste0("Number of unique other responses: ", length(unique(tolower(k.data$other_inst))) - 1)
unique(tolower(k.data$other_inst[!is.na(k.data$other_inst)]))
```

##### Original options and cleaned groupings:

| code         | full text                                           | field_cleaned        |
| ------------ | --------------------------------------------------- | -------------------- |
| univ         | University (public / private)                       | University           |
| ngo          | NGO / Association                                   | NGO                  |
| gov_pub_agen | Government ministry / Government agency             | Governmental Agency  |
| lab          | Laboratory / Research center / Research group       | Research Institution |
| priv_inst    | Private company                                     | Private Company      |
| none         | None of the above                                   | Independent          |

```{r 3.03B, echo = FALSE}
#Replacing other responses with code from original options
k.data <- k.data %>% mutate(other_inst = tolower(other_inst)) %>%
  mutate(other_inst = recode(other_inst,
    "protection de l'environnement" = "univ",
    "pnud/gef"                      = "ngo",
    "independent"                   = "none",
    "homeopharma"                   = "priv_inst",
    "ist ampasampito"               = "univ",
    "ist"                           = "univ",
    "stem4good"                     = "ngo",
    "ird"                           = "lab",
    "private high school"           = "priv_inst",
    "ips"                           = "ngo",
    "centre de recherches"          = "lab",
    "bureau d'étude"                = "priv_inst",
    "organisme international"       = "ngo",
    "société  civil"                = "gov_pub_agen"
    ))
```

##### Creating cleaned, standardized columns (1s and 0s for each option)

##### Cleaned codes

| code         | code_cleaned | field_cleaned        |
| ------------ | -------------|--------------------- |
| univ         | inst_uni     | University           |
| ngo          | inst_ngo     | NGO                  |
| gov_pub_agen | inst_gov     | Governmental Agency  |
| lab          | inst_lab     | Research Institution |
| priv_inst    | inst_priv    | Private Company      |
| none         | inst_none    | Independent          |

***

Criteria:

***

Type of institution = University `inst_uni`: 

  1. selected institution as university (`inst/univ` == "1")
  2. selected other institution but other response is university (`other_inst == "univ"`)
  3. selected academic stage as masters or PhD student: (`student_ms` == "1" | `student_phd` == "1")

***

Type of institution = NGO `inst_ngo`: 
  1. selected institution as ngo (`inst/ngo` == "1")
  2. selected institution as association (`inst/assoc` == "1")
  3. selected other institution but other response is ngo (`other_inst == "ngo"`)

***

Type of institution = Governmental Agency `inst_gov`: 
  1. selected institution as gov (`inst/gov_pub_agen` == "1")
  2. selected other institution but other response is gov (`other_inst == "gov_pub_agen"`)

***

Type of institution = Research Institution `inst_lab`: 
  1. selected institution as lab or research center (`inst/lab` == "1")
  2. selected other institution but other response is gov (`other_inst == "lab"`)

***

Type of institution = Private company `inst_priv`: 
  1. selected institution as private company (`inst/priv_inst` == "1")
  2. selected other institution but other response is private company (`other_inst == "priv_inst"`)

***

Type of institution = None / Independent `inst_none`: 
  1. no other institution type selected (`inst_uni != 1 & inst_ngo != 1 & inst_gov != 1 & inst_lab != 1 & inst_priv != 1`)

***

```{r 3.03C, echo = FALSE}
k.data <- k.data %>%
  #inst_uni
  mutate(inst_uni = case_when(
    `inst/univ`  == "1"    ~ 1,
     other_inst  == "univ" ~ 1,
     student_ms  == "1"    ~ 1,
     student_phd == "1"    ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #inst_ngo
  mutate(inst_ngo = case_when(
    `inst/ngo`   == "1"   ~ 1,
    `inst/assoc` == "1"   ~ 1,
     other_inst  == "ngo" ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #inst_gov
  mutate(inst_gov = case_when(
    `inst/gov_pub_agen` == "1"            ~ 1,
     other_inst         == "gov_pub_agen" ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #inst_lab
  mutate(inst_lab = case_when(
    `inst/lab` == "1"        ~ 1,
     other_inst     == "lab" ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #inst_priv
  mutate(inst_priv = case_when(
    `inst/priv_inst` == "1"         ~ 1,
     other_inst      == "priv_inst" ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #inst_none
  group_by(index) %>% mutate(inst_none = case_when(
     sum(inst_uni, inst_ngo, inst_gov, inst_lab, inst_priv, na.rm = TRUE) < 1 ~ 1,
     is.na(inst) ~ NA_real_,
     TRUE ~ 0)) %>% ungroup() %>%
  #Removing old institution type columns
  select(start:affiliation, inst_uni, inst_ngo, inst_gov, inst_lab, inst_priv, inst_none, office_build:index)
```



***

**4. Challenges to attend online opportunities**

- Listing other responses

```{r 3.04A, echo = FALSE}
paste0("Number of unique other responses: ", length(unique(tolower(k.data$other_challenge_opport))) - 1)
#converting to lower case, ordering by length of response
v.sor.4 <- unique(tolower(k.data$other_challenge_opport[!is.na(k.data$other_challenge_opport)]))
v.sor.4[order(nchar(v.sor.4), v.sor.4)]
```

##### Original options and cleaned groupings:

| code               | full text                     | field_cleaned            |
| ------------------ | ----------------------------- | ------------------------ |
| cost               | Costs                         | Cost                     |
| internet           | Internet access issues        | Internet Access          |
| elect              | Electricity access issues     | Electricity              |
| nocomput           | No personal computer          | Computer Access          |
| compissue          | Computer issues               | Computer Issues          |
| lackspace          | Lack of a space at home       | Lack of Space            |
| unawareoffer       | Unaware of interesting offers | Unaware of Offers        |
| lacktime           | Lack of time                  | Lack of Time             |
| language           | Language barriers             | Language Barrier         |
| anxiety_notmotiv   | Anxiety or other distractions | Anxiety and distractions |
| timezone           | Difference in time zone       | Time zone                |
| anxiety_notinteres | Not interested                | Uninterested             |
| none               | None of the above             | None                     |

```{r 3.04B, echo = FALSE}
#Replacing other responses with code from original options
k.data <- k.data %>% mutate(other_challenge_opport = tolower(other_challenge_opport)) %>%
  mutate(other_challenge_opport = recode(other_challenge_opport,
    "tsy fahaizana teny hafa"                                         = "language",
    "limitation de possibilite"                                       = "unawareoffer",
    "non maitrise des protocoles"                                     = "compissue",
    "cost of the internet connexion"                                  = "internet",
    "limitation du nombre de participants"                            = "unawareoffer",
    "problème des manipulation des logiciel informatique"             = "compissue",
    "perturbation à domicile à cause de la presence de vie familiale" = "lackspace",
    "voisins et entourage bruyants, source d'incompréhension et de malaise vis à vis des interlocuteurs"  = "lackspace",
    #09 May 2021 Update
    "manque de formation"                             = "compissue",
    "sûreté de la formation"                          = "compissue",
    "report de date de formation à cause du covid-19" = "unawareoffer"
    ))
```

##### Cleaned codes

| code               | code_cleaned | field_cleaned            |
| ------------------ | ------------ | ------------------------ |
| cost               | access_cost  | Cost                     |
| internet           | access_wifi  | Internet Access          |
| elect              | access_elec  | Electricity              |
| nocomput           | acess_comp   | Computer Access          |
| compissue          | comp_issue   | Computer Issues          |
| lackspace          | access_space | Lack of Space            |
| unawareoffer       | access_aware | Unaware of Offers        |
| lacktime           | access_time  | Lack of Time             |
| language           | lang_barrier | Language Barrier         |
| anxiety_notmotiv   | anx_motiv    | Anxiety and distractions |
| timezone           | time_zone    | Time zone                |
| anxiety_notinteres | uninterested | Uninterested             |
| none               | chall_none   | None                     |

***

Criteria:

***

For each, the respondent either selected that challenge to online activities or selected other but their response is categorized as that challenge. For example, for cost:

Challenge to online activities = Cost `access_cost`: 
  1. selected cost (`challenge_opport/cost` == "1")
  2. selected other but other response is cost (`other_challenge_opport == "cost"`)

***

```{r 3.04C, echo = FALSE}
k.data <- k.data %>%
  mutate(access_cost = case_when(
    `challenge_opport/cost` == "1"    ~ 1,
     other_challenge_opport == "cost" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(access_wifi = case_when(
    `challenge_opport/internet` == "1"    ~ 1,
     other_challenge_opport     == "internet" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>%
  mutate(access_elec = case_when(
    `challenge_opport/elect` == "1"     ~ 1,
     other_challenge_opport  == "elect" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(acess_comp = case_when(
    `challenge_opport/nocomput` == "1"        ~ 1,
     other_challenge_opport     == "nocomput" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(comp_issue = case_when(
    `challenge_opport/compissue` == "1"          ~ 1,
     other_challenge_opport       == "compissue" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(access_space = case_when(
    `challenge_opport/lackspace` == "1"         ~ 1,
     other_challenge_opport      == "lackspace" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(access_aware = case_when(
    `challenge_opport/unawareoffer` == "1"            ~ 1,
     other_challenge_opport         == "unawareoffer" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(access_time = case_when(
    `challenge_opport/lacktime` == "1"    ~ 1,
     other_challenge_opport     == "lacktime" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(lang_barrier = case_when(
    `challenge_opport/language` == "1"        ~ 1,
     other_challenge_opport     == "language" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(anx_motiv = case_when(
    `challenge_opport/anxiety_notmotiv` == "1"                ~ 1,
     other_challenge_opport             == "anxiety_notmotiv" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(time_zone = case_when(
    `challenge_opport/timezone` == "1"        ~ 1,
     other_challenge_opport     == "timezone" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  mutate(uninterested = case_when(
    `challenge_opport/anxiety_notinteres` == "1"                  ~ 1,
     other_challenge_opport               == "anxiety_notinteres" ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% 
  #chall_none
  group_by(index) %>% mutate(chall_none = case_when(
     sum(access_cost, access_wifi, access_elec, acess_comp, comp_issue, access_space, 
         access_aware, access_time, lang_barrier, anx_motiv, time_zone, uninterested, na.rm = TRUE) < 1 ~ 1,
     is.na(challenge_opport) ~ NA_real_,
     TRUE ~ 0)) %>% ungroup() %>%
  #Removing old online activity challange columns
  select(start:opport_virtual_current,
         access_cost, access_wifi, access_elec, acess_comp, comp_issue, access_space, 
         access_aware, access_time, lang_barrier, anx_motiv, time_zone, uninterested,
         cohab_status:index)
```



***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 4 | Progress summaries: Summary stats and sampling time series

</div>

***
***

- Summary of sampling progress listed:

```{r 4.01, echo = FALSE}
paste0("Dates of surveys completed:")
paste0(sort(unique(k.data$today)))
paste0("Number of surveys completed (n) = ", length(k.data$agreement[k.data$agreement == "yes"]))
paste0("Number of surveys completed, female = ", 
       length(k.data$agreement[k.data$agreement == "yes" & k.data$gender == "female"]))
paste0("Number of surveys completed, male  = ", 
       length(k.data$agreement[k.data$agreement == "yes" & k.data$gender == "male"]))
paste0("Number of surveys completed, nonbinary gender = ", 
       length(k.data$agreement[!is.na(k.data$gender) & k.data$gender == "other_notsay"]))
paste0("Average number of surveys performed per day of sampling = ",
       round(length(k.data$agreement[k.data$agreement == "yes"])/length(unique(k.data$today)), 2))
```

- Summary of sampling progress, time series plot:
```{r 4.02, echo = FALSE}
p.gender_summary1 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  summarize(n = length(today), .groups = "drop") %>%
  ggplot(aes(x = today, y = n)) +
  geom_bar(stat='identity', width=0.8) +
  xlab("Date") + labs(subtitle = "Sampling by day") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p.gender_summary2 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  count(gender) %>% ungroup() %>%
  ggplot(aes(x = today, y = n, fill = gender)) +
  geom_bar(stat='identity', width=0.8) +
  xlab("Date") + 
  labs(subtitle = "Sampling by day and gender",
       fill = "") +
  scale_fill_manual(values  = c("#46055E", "#468D8A", "#F2DE24"), 
                     labels = c("Female", "Male", "Prefer not to say\nor nonbinary")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "right")

p.gender_summary3 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  summarize(n = length(today), .groups = "drop") %>% 
  mutate(n_cum = cumsum(n)) %>%
  ggplot(aes(x = today, y = n_cum)) +
  geom_bar(stat='identity', width=0.8, fill = "#ff6f00") +
  xlab("Date") + ylab ("Cumulative number of surveys completed") + labs(subtitle = "Cumulative Sampling by day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

```{r 4.03, fig.height = 7, fig.width = 10}
grid.arrange(p.gender_summary1, p.gender_summary2, nrow = 1)
```

```{r 4.04, fig.height = 7, fig.width = 10}
p.gender_summary3
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 5 | Preliminary data visualizations: Impact on research activitiy by gender

</div>

***
***


```{r 5.01, echo = FALSE}
d.rae <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay")

p.rae.fieldNA <- d.rae %>% 
  group_by(gender) %>% count(fieldwork_affect) %>% ungroup() %>%
  mutate(fieldwork_affect = factor(fieldwork_affect, 
                                   levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  ggplot(aes(x = gender, y = n, fill = fieldwork_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Affects on fieldwork by gender (with NAs)") + 
  xlab("Sex") + ylab("Proportion") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = "right")

p.rae.writeNA <- d.rae %>% 
  group_by(gender) %>% count(writ_affect) %>% ungroup() %>%
  mutate(writ_affect = factor(writ_affect, 
                              levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  ggplot(aes(x = gender, y = n, fill = writ_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Affects on writing by gender (with NAs)") + 
  xlab("Sex") + ylab("Proportion") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = "right")

```

**Figure 5A** Impacts of COVID-19 disruptions on fieldwork and writing by gender (including those that responded "not applicable")
```{r 5.02, fig.height=7, fig.width=10, echo=FALSE}
grid.arrange(p.rae.fieldNA, p.rae.writeNA, nrow = 1)
```

- Writing a function to create the plot for a desired research activity (e.g., `fieldwork_affect`)

```{r 5.03, echo = FALSE}
f.plot.res_act <- function(dataset, activity, activity_name){

  d.res_act <- dataset %>% select(gender, activity) %>% drop_na(gender) %>% filter(gender != "other_notsay")
  names(d.res_act) <- c("gender", "selected_activity")
  d.res_act <- d.res_act %>% group_by(gender) %>% count(selected_activity) %>% ungroup() %>%
    mutate(selected_activity = factor(selected_activity, 
                                      levels = rev(c("na", 
                                                     "nochangeaffect", 
                                                     "slightaffect", 
                                                     "modaffect",
                                                     "veryaffect")))) %>%
    filter(selected_activity != "na")

  p.res_act <- d.res_act %>% ggplot(aes(x = gender, y = n, fill = selected_activity)) +
    geom_bar(position="fill", stat='identity', width=0.8) +
    labs(title = activity_name,
         subtitle = paste0("Impact by gender among\napplicable respondents\n", "n = ", sum(d.res_act$n))) +
    xlab("Gender") + ylab("Proportion") +
    scale_fill_viridis_d(option = "inferno", direction = -1, name = "Impact: ", 
                         labels = c("Strong", "Moderate", "Slight", "None")) +
    theme_bw() +
    theme(#legend.position = "bottom", 
          legend.position = "none",
          legend.title = element_text(size = 5), 
          legend.text = element_text(size = 5))
  
  return(p.res_act)
}
```


**Figure 5B** Impacts of COVID-19 disruptions on fieldwork, writing, and data analysis activity among Malagasy STEM by gender
(for those respondents identifying these as applicable activities for their work or studies)

```{r 5.04, echo = FALSE}
p.rae.field <- f.plot.res_act(dataset = k.data, activity = "fieldwork_affect", activity_name = "Fieldwork")
p.rae.write <- f.plot.res_act(dataset = k.data, activity = "writ_affect",      activity_name = "Writing")
p.rae.datan <- f.plot.res_act(dataset = k.data, activity = "data_affect",      activity_name = "Data Analysis")

grid.arrange(p.rae.field, p.rae.write, p.rae.datan, nrow = 1)
```




***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 6 | Preliminary data visualizations: Ranked stressors by gender

</div>

***
***

(using "slopegraphs": [example](https://charliepark.org/slopegraphs/), [example](https://acaird.github.io/computers/r/2013/11/27/slopegraphs-ggplot), [example](https://ibecav.github.io/slopegraph/))

Questionnaire Section 6: Stress during the coronavirus pandemic

- 1) Did you experience increased stress that related to your efficiency at work (e.g., procrastination, deadlines)? `stress_delaywork`
- 2) Did you experience increased stress related to your future career plans? `stress_career`
- 3) Did you experience increased stress related to the burden of childcare and household work? `stress_burden`
- 4) Did you experience increased stress related to your personal relationships or marriage? `stress_relation`
- 5) Did you experience increased stress related to pregnancy / access to birth control / family planning? `stress_pregbirth`
- 6) Did you experience increased stress associated with money issues (e.g., paying bills)? `stress_moneyemplo`
- 7) Did you experience increased stress related to your personal health? `stress_pershealth`
- 8) Did you experience increased stress related to the health of your family members? `stress_healthfam`
- 9) Did you experience increased stress related to social anxiety: loneliness, lack of social interaction, lack of personal space, depression, lack of physical activity? `stress_anxiety`


- Preparing data for plotting
```{r 6.01, echo=FALSE}
#Selecting relevant columns, dropping NAs, and nonbinary gender respondents (because n = 3)
df.stress <- k.data %>% select(year_of_birth:degree, stress_delaywork:stress_relation, stress_moneyemplo:stress_anxiety) %>% 
  drop_na() %>%
  filter(gender != "other_notsay")
#Calculating the percent of respondents with moderate, strong, or extreme stress (p.ss) for each topic
df.stress.all <- df.stress %>% group_by(gender) %>% summarize(
  p.ss.delaywork  = length(which(stress_delaywork %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_delaywork),
  p.ss.career     = length(which(stress_career %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_career),
  p.ss.burden     = length(which(stress_burden %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_burden),
  p.ss.relation   = length(which(stress_relation %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_relation),
  p.ss.moneyemplo = length(which(stress_moneyemplo %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_moneyemplo),
  p.ss.pershealth = length(which(stress_pershealth %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_pershealth),
  p.ss.healthfam  = length(which(stress_healthfam %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_healthfam),
  p.ss.anxiety    = length(which(stress_anxiety %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_anxiety), .groups = "drop") %>%
  melt(id.vars = "gender")
#Adding more presentable labels
df.stress.all <- df.stress.all %>% mutate(label = case_when(
  variable == "p.ss.delaywork"  ~ "Interruptions/delays at work",
  variable == "p.ss.career"     ~ "Future career plans",
  variable == "p.ss.burden"     ~ "Burden of household work",
  variable == "p.ss.relation"   ~ "Personal relationships",
  variable == "p.ss.moneyemplo" ~ "Money/financial responsibilities",
  variable == "p.ss.pershealth" ~ "Personal health",
  variable == "p.ss.healthfam"  ~ "Health of family members",
  variable == "p.ss.anxiety"    ~ "Anxiety or social stress"))
```

- Plotting
```{r 6.02, fig.height=7, fig.width=10, echo=FALSE}
#Putting all the thematic changes to the plot in a list:
MySpecial <- list(  
  # move the x axis labels up top
  scale_x_discrete(position = "top"),
  theme_bw(),
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none"),
  # Remove the panel border
  theme(panel.border     = element_blank()),
  # Remove just about everything from the y axis
  theme(axis.title.y     = element_blank()),
  theme(axis.text.y      = element_blank()),
  theme(panel.grid.major.y = element_blank()),
  theme(panel.grid.minor.y = element_blank()),
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()),
  theme(panel.grid.major.x = element_blank()),
  theme(axis.text.x.top      = element_text(size=12)),
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()),
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)),
  theme(plot.subtitle    = element_text(hjust = 0.5))
)

p.rs <- ggplot(data = df.stress.all, aes(x = gender, y = value, group = variable)) +
  geom_line(aes(color = variable, alpha = 1), size = 1) +
  geom_point(aes(color = variable, alpha = 1), size = 3) +
  geom_text_repel(data = df.stress.all %>% filter(gender == "female"), 
                  aes(label = paste0(label, " : ", round(value*100, 2), "%")) , 
                  hjust = "right", 
                  size = 3, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text_repel(data = df.stress.all %>% filter(gender == "male"), 
                  aes(label = paste0(round(value*100, 2), "%")) , 
                  hjust = "right", 
                  size = 3, 
                  nudge_x = .5, 
                  direction = "y") +
  MySpecial +
  labs(
    title    = "Percent of respondents reporting moderate or greater stress related to:",
    ##Storing sample size as a variable to use in the caption to the plot below
    subtitle = paste0("n = ", length(df.stress$year_of_birth)),
    caption  = "Madagascar STEM students and professionals"
  )

p.rs
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 7 | Preliminary data visualizations: Household crowding and age patterns

</div>

***
***

- Selected questions from the survey:

  - 4.04 Not including bathrooms or kitchen, how many rooms does the house you live in have? `nb_room`

  - 4.06 Household members `hh_member_count` : `age_hh_member`, `age_hh_member_001`:`age_hh_member_014`

***

- Preparing the data for plotting

```{r 7.01, echo=FALSE}
df.hhc <- k.data %>% 
  #Selecting relevant columns
  select(index, year_of_birth, gender, region,
         nb_room,
         hh_member_count,
         close_contact) %>%
  #Converting columns to numeric
  mutate(year_of_birth = as.numeric(year_of_birth), nb_room = as.numeric(nb_room), hh_member_count = as.numeric(hh_member_count)) %>%
  #Adding 1 to the hh size (to include the respondent + the other members of the household)
  mutate(hh_member_count = hh_member_count + 1) %>%
  #Calculating approximate age of the respondent and storing as age_hh_memb_i
  mutate(age_hh_memb_i = 2021-year_of_birth) %>%
  #Using join to add the columns containing ages of the other household members
  #Doing separately so can convert all columns to numeric using mutate_if()
  full_join(k.data %>% 
              #renaming the column with the age of the first other household member (the 2nd member of the household)
              # age_hh_memb_000
              mutate(age_hh_memb_000 = age_hh_memb) %>%
              select(index, age_hh_memb_000, age_hh_memb_001:age_hh_memb_014) %>% 
              mutate_if(is.character, as.numeric),
            by = "index") %>%
  #Subsetting to Antananarivo region Analamanga
  filter(region == "analamang") %>%
  #Removing illogical responses (e.g., 0 rooms in the house, negative number of hh members)
  #(e.g. hh_member count > 14 because didn't record ages for more than 14 individuals)
  filter(nb_room > 0) %>% filter(hh_member_count > 0) %>% filter(hh_member_count < 15) %>%
  #Calculating the number of people per room in houses
  mutate(pers_per_room = hh_member_count/nb_room) %>%
  #Determining which records have full household age data and removing incomplete records
  mutate(cols_w_age = 1 + rowSums(!is.na(select(., age_hh_memb_000:age_hh_memb_014))),
         hh_diff = hh_member_count - cols_w_age) %>%
  #Removing households that did not report the age of each member
  filter(hh_diff < 1) %>%
  #Calculating the age of eldest individual
  rowwise() %>% mutate(max_age = max(c(age_hh_memb_i, 
                                       age_hh_memb_000, age_hh_memb_001, age_hh_memb_002, age_hh_memb_003,
                                       age_hh_memb_004, age_hh_memb_005, age_hh_memb_006, age_hh_memb_006,
                                       age_hh_memb_007, age_hh_memb_008, age_hh_memb_009, age_hh_memb_010,
                                       age_hh_memb_011, age_hh_memb_012, age_hh_memb_013, age_hh_memb_014),
                                     na.rm = TRUE)) %>% ungroup() %>%
  #Ordering by household size and age of eldest
  arrange(hh_member_count, max_age) %>%
  #Giving a rank for plotting (index_hh) that restarts at 1 for each household size
  group_by(hh_member_count) %>% mutate(index_hh = 1:length(index)) %>% ungroup() %>%
  #Melting so each individual is on a row
  melt(id.vars = c("index", "index_hh", "year_of_birth", "gender", "region",
                   "nb_room", "hh_member_count", "close_contact",
                   "pers_per_room", "cols_w_age", "hh_diff", "max_age")) %>%
  #For plotting with a different color, adding a marker for individuals 65 and older
  mutate(old = as.factor(ifelse(max_age > 64, 1, 0))) %>%
  #Deleting rows with incomplete data
  drop_na()
```

***

- Plotting the household size distribution

```{r 7.02, fig.height=7, fig.width=10, echo=FALSE}
#Highlighting households with individuals over 65
p.hhc <- df.hhc %>% ggplot(aes(x = value, y = index_hh, color = old)) +
  geom_point() +
  #Separating each household size
  facet_grid(~ hh_member_count, scales = "fixed") +
  xlab("Age of household members") + ylab("Household") +
  scale_color_manual(values = c("black", "#c51162"), 
                     labels = c("Housholds with 0 individuals > 65        ", "Households with 1+ individual > 65")) +
  theme_bw() +
  scale_y_continuous(breaks = c(1:max(df.hhc$index_hh)+1)) +
  rremove("y.text") +
  labs(
    title    = "Age distribution of households in Analamanga region, Madagascar",
    subtitle = paste0("n = ", length(unique(df.hhc$index)), " households",
                      "\nSeparated into panels by household size; Each row shows one household of the specified size"),
    caption  = "Households containing Madagascar STEM student or professional",
    color = "") + 
  theme(legend.position = "top")

p.hhc
```

- Plotting a histogram of the number of individuals per room for Analamanga

```{r 7.03, fig.height=7, fig.width=10, echo=FALSE}
#Keeping the pers_per_room from the melted df.hhc
df.hhc %>% group_by(index) %>% summarize(pers_per_room = max(pers_per_room), .groups = "drop") %>%
  ggplot(aes(x = pers_per_room)) +
  geom_bar(fill = "#00695c") +
  scale_x_binned() +
  xlab("Number of individuals per room in the house \n (excluding bathrooms and kitchen)") +
  ylab("Count") + theme_minimal()
```



