---
title: "Weekly_Data_Processing"
author: "Benny Rice"
date: "2/8/2021"
output: html_document
---

```{r setup, include = FALSE, eval = TRUE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

***
***
<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

## HEADER INFO

- Benny Rice | Department of Ecology and Evolutionary Biology | Princeton University | b.rice@princeton.edu
- Code associated with processing data from the **Impacts of Covid-19 on Malagasy STEM** project
- Apologies in advance for amateurish code (ie all the loops and clunkiness)
- In colloboration with Lova Marline, Miary Raselimanana, Seheno Andriantsaralaza, Hervet Randriamady

</div>

***

(Set up: Loading necessary libraries)
```{r i1, message = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(reshape2)
library(ggpubr)
library(ggalt)
library(ggrepel)
library(here)
library(gridExtra)
library(readxl)
```

***
***

#### OUTLINE:

- **Section 1 |** Reading in data downloaded from Kobo Collect
- **Section 2 |** Cleaning data (in progress)
- **Section 3 |** Progress summaries: Summary stats and sampling time series
- **Section 4 |** Preliminary data visualizations: Breakdown by gender
- **Section 5 |** ...



**FIX** Update outline at the end (add figures and tables interspersed ^)


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 1 | Reading in data downloaded from Kobo Collect (xls form, English)

</div>

***
***

- Data is read from an xlsx file that is manually downloaded from the Kobo Collect account
  - [KoBoToolbox](https://kf.kobotoolbox.org/#/forms) --> `Impacts of Covid-19 on Malagasy STEM` --> `DATA` --> `Downloads`
  - Selecting export options:
    - Export type `XLS`
    - Value and header format `XML values and headers`
    - `Advanced options`: Do NOT select `Include fields from all 31 deployed versions`
  - Manually uploading to [the GitHub repository for this project](https://github.com/labmetcalf/COVID_STEM_MADA)
- Data file name should include the date at which data was downloaded

```{r 1.01}
k.data <- read_xlsx(here("DATA_05_Impacts_of_Covid-19_on_Malagasy_STEM_-_latest_version_-_False_-_2021-04-22-14-19-13.xlsx"))
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 2 | Cleaning data (in progress)

</div>

***
***

- Cleaning up "other" responses for:
  - field of study (`other_field`)
  - academic stage / position (`other_acad`)
  - type of institution (`other_inst`)
  - challenges  to attend online opportunities (`other_challenge_opport`)
  
- Changing text responses by hardcoding following the tables below

**Field of study**

- Listing other responses

```{r 2.01.1, echo = FALSE}
paste0("Number of other responses: ", length(unique(k.data$other_field)) - 1)
unique(k.data$other_field[!is.na(k.data$other_field)])
```

- Notes:
  - Agronomic Sciences and Agriculture & Natural Resources can probably be combined

| Num | raw response text                                   | cleaned text                                     |
| --- | --------------------------------------------------- | ------------------------------------------------ |
| 01  | "HYDROSCIENCES"                                     | "Atmospheric Sciences, Earth and Ocean Sciences" |
| 02  | "Sciences Agronomiques"                             | "Agronomic Sciences"                             |
| 03  | "Sciences agronomiques"                             | "Agronomic Sciences"                             |
| 04  | "sciences agronomiques"                             | "Agronomic Sciences"                             |
| 05  | "SCIENCES AGRONOMIQUES"                             | "Agronomic Sciences"                             |
| 06  | "Pharmacologie"                                     | "Pharmacology, Physiology & Cosmetology"         |
| 07  | "pharmacologie"                                     | "Pharmacology, Physiology & Cosmetology"         |
| 08  | "Pharmacology"                                      | "Pharmacology, Physiology & Cosmetology"         |
| 09  | "Pharmacologie et Cosmétologie"                     | "Pharmacology, Physiology & Cosmetology"         |
| 10  | "PHARMACOLOGIE"                                     | "Pharmacology, Physiology & Cosmetology"         |
| 11  | "Pharmarmacologie, cosmetic"                        | "Pharmacology, Physiology & Cosmetology"         |
| 12  | "Nutrition"                                         | "Health Sciences"                                |
| 13  | "Sciences et technique nucleaires"                  | "Physics"                                        |
| 14  | "Sciences nucleaires, physiques, nanotechnologie"   | "Physics"                                        |
| 15  | "Sciences et techniques nucléaires"                 | "Physics"                                        |
| 16  | "Sciences techniques nucleaires et nanotechnologie" | "Physics"                                        |
| 17  | "Ecotourism science"                                | "Agriculture & Natural Resources"                |
| 18  | "Paléontologie"                                     | "Biological Sciences"                            |

```{r 2.01.1, echo = FALSE}
#Replacing other responses with standard text
#k.data <- k.data %>% mutate(field = recode(ifesle(field == "Sciences et technique nucleaires", "Physics", NA)) 

#mutate(sex=recode(sex, 
#                         `1`="Male",
#                         `2`="Female"))
```


**Academic stage / position**

Listing other responses
```{r 2.02, echo = FALSE}
paste0("Number of other responses: ", length(unique(k.data$other_acad)) - 1)
unique(k.data$other_acad[!is.na(k.data$other_acad)])
```
- Notes:
  - What is the difference between Consultant, Independent researcher, and Research officer?
  - Research assistant should be changed to Research assistant or technician
  - Add "Principal investigator" or "Research group leader" to Professor etc
  - Need to check respondent's responses to other questions for some to see what level they are at

| Num | raw response text                        | cleaned text                                          |
| --- | ---------------------------------------- | ----------------------------------------------------- |
| 01  | "Cadre dans une Entreprise"              | ???                                                   |
| 02  | "Enseignant-chercher (vacataire)"        | ???                                                   |
| 03  | "Technicien de laboratoire"              | "Research assistant"                                  |
| 04  | "Enseignant vacataire,   consultant"     | "Consultant"                                          |
| 05  | "Médecin"                                | ??? Post doctoral researcher?                         |
| 06  | "I am recently graduated and would ..."* | ???                                                   |
| 07  | "Medicin"                                | ??? Post doctoral researcher?                         |
| 08  | "Professeur"                             | "Faculty member, Professor, or University Instructor" |
| 09  | "etudiante en licence"                   | ??? Should they be eligible?                          |
| 10  | "Directeur Général"                      | "Faculty member, Professor, or University Instructor" |
| 11  | "Président GERP"                         | "Faculty member, Professor, or University Instructor" |
| 12  | "Fonctionnaire de l'état"                | ???                                                   |
| 13  | "Professeur titulaire"                   | "Faculty member, Professor, or University Instructor" |
| 14  | "CLO Multidisciplinaire"                 | ???                                                   |
| 15  | "Formation spécialisée"                  | ???                                                   |



***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 3 | Progress summaries: Summary stats and sampling time series

</div>

***
***

- Summary of sampling progress listed:

```{r 3.01, echo = FALSE}
paste0("Dates of surveys completed:")
paste0(sort(unique(k.data$today)))
paste0("Number of surveys completed (n) = ", length(k.data$agreement[k.data$agreement == "yes"]))
paste0("Number of incomplete or aborted surveys = ", sum(is.na(k.data$gender)))
paste0("Number of surveys completed, female = ", 
       length(k.data$agreement[k.data$agreement == "yes" & k.data$gender == "female"]))
paste0("Number of surveys completed, male  = ", 
       length(k.data$agreement[k.data$agreement == "yes" & k.data$gender == "male"]))
paste0("Number of surveys completed, nonbinary gender = ", 
       length(k.data$agreement[!is.na(k.data$gender) & k.data$gender == "other_notsay"]))
paste0("Average number of surveys performed per day of sampling = ",
       length(k.data$agreement[k.data$agreement == "yes"])/length(unique(k.data$today)))
```

- Summary of sampling progress, time series plot:
```{r 3.02, echo = FALSE}
p.gender_summary1 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  summarize(n = length(today), .groups = "drop") %>%
  ggplot(aes(x = today, y = n)) +
  geom_bar(stat='identity', width=0.8) +
  xlab("Date") + labs(subtitle = "Sampling by day") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p.gender_summary2 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  count(gender) %>% ungroup() %>%
  ggplot(aes(x = today, y = n, fill = gender)) +
  geom_bar(stat='identity', width=0.8) +
  xlab("Date") + labs(subtitle = "Sampling by day and gender") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "right")

p.gender_summary3 <- k.data %>% drop_na(gender) %>% select(agreement, today, gender) %>% group_by(today) %>% 
  summarize(n = length(today), .groups = "drop") %>% 
  mutate(n_cum = cumsum(n)) %>%
  ggplot(aes(x = today, y = n_cum)) +
  geom_bar(stat='identity', width=0.8, fill = "#ff6f00") +
  xlab("Date") + ylab ("Cumulative number of surveys completed") + labs(subtitle = "Cumulative Sampling by day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

```{r 3.03, fig.height = 7, fig.width = 10}
grid.arrange(p.gender_summary1, p.gender_summary2, nrow = 1)
```

```{r 3.04, fig.height = 7, fig.width = 10}
p.gender_summary3
```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 4 | Preliminary data visualizations: Breakdown by gender

</div>

***
***

Plotting research activity affects by gender
```{r 4.01, echo = FALSE}
p.301a <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay") %>% 
  group_by(gender) %>% count(fieldwork_affect) %>% ungroup() %>%
  mutate(fieldwork_affect = factor(fieldwork_affect, 
                                   levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  ggplot(aes(x = gender, y = n, fill = fieldwork_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Affects on fieldwork by gender (with NAs)") + xlab("Sex") + ylab("Proportion") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = "right")

p.301b <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay") %>% 
  group_by(gender) %>% count(writ_affect) %>% ungroup() %>%
  mutate(writ_affect = factor(writ_affect, 
                              levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  ggplot(aes(x = gender, y = n, fill = writ_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Affects on writing by gender (with NAs)") + xlab("Sex") + ylab("Proportion") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(legend.position = "right")

p.301c <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay") %>% 
  group_by(gender) %>% count(fieldwork_affect) %>% ungroup() %>%
  mutate(fieldwork_affect = factor(fieldwork_affect, 
                                   levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  filter(fieldwork_affect != "na") %>%
  ggplot(aes(x = gender, y = n, fill = fieldwork_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Impacts on fieldwork by gender\n(among applicable respondents)") + 
  xlab("Gender") + ylab("Proportion") +
  scale_fill_viridis_d(option = "inferno", direction = -1, name = "Impact: ", 
                       labels = c("Strong", "Moderate", "Slight", "None")) +
  theme_bw() +
  theme(legend.position = "top", legend.title = element_text(size = 5), legend.text = element_text(size = 5))

p.301d <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay") %>% 
  group_by(gender) %>% count(writ_affect) %>% ungroup() %>%
  mutate(writ_affect = factor(writ_affect, 
                                   levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  filter(writ_affect != "na") %>%
  ggplot(aes(x = gender, y = n, fill = writ_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Impacts on writing by gender\n(among applicable respondents)") + 
  xlab("Gender") + ylab("Proportion") +
  scale_fill_viridis_d(option = "inferno", direction = -1, name = "Impact: ", 
                       labels = c("Strong", "Moderate", "Slight", "None")) +
  theme_bw() +
  theme(legend.position = "top", legend.title = element_text(size = 5), legend.text = element_text(size = 5))


p.301e <- k.data %>% select(gender, fieldwork_affect:editpeer_affect) %>% drop_na(gender) %>% 
  filter(gender != "other_notsay") %>% 
  group_by(gender) %>% count(data_affect) %>% ungroup() %>%
  mutate(data_affect = factor(data_affect, 
                                   levels = rev(c("na", "nochangeaffect", "slightaffect", "modaffect", "veryaffect")))) %>%
  filter(data_affect != "na") %>%
  ggplot(aes(x = gender, y = n, fill = data_affect)) +
  geom_bar(position="fill", stat='identity', width=0.8) +
  labs(subtitle = "Impacts on data analysis by gender\n(among applicable respondents)") +
  xlab("Gender") + ylab("Proportion") +
  scale_fill_viridis_d(option = "inferno", direction = -1, name = "Impact: ", 
                       labels = c("Strong", "Moderate", "Slight", "None")) +
  theme_bw() +
  theme(legend.position = "top", legend.title = element_text(size = 5), legend.text = element_text(size = 5))

```


**Figure 4.02** Impacts of COVID-19 disruptions on fieldwork and writing by gender (including those that responded "not applicable")
```{r 4.02, fig.height=7, fig.width=10, echo=FALSE}
grid.arrange(p.301a, p.301b, nrow = 1)
```


**Figure 4.03 Impacts of COVID-19 disruptions on fieldwork, writing, and data analysis activity among Malagasy STEM by gender**
(for those respondents identifying these as applicable activities for their work or studies)

```{r 4.03, fig.height=7, fig.width=10, echo=FALSE}
grid.arrange(p.301c, p.301d, p.301e, nrow = 1)
```



***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 5 | Preliminary data visualizations: Ranked stressors by gender

</div>

***
***

(using "slopegraphs": [example](https://charliepark.org/slopegraphs/), [example](https://acaird.github.io/computers/r/2013/11/27/slopegraphs-ggplot), [example](https://ibecav.github.io/slopegraph/))

Section 6: Stress during the coronavirus pandemic

- 1) Did you experience increased stress that related to your efficiency at work (e.g., procrastination, deadlines)? `stress_delaywork`
- 2) Did you experience increased stress related to your future career plans? `stress_career`
- 3) Did you experience increased stress related to the burden of childcare and household work? `stress_burden`
- 4) Did you experience increased stress related to your personal relationships or marriage? `stress_relation`
- 5) Did you experience increased stress related to pregnancy / access to birth control / family planning? `stress_pregbirth`
- 6) Did you experience increased stress associated with money issues (e.g., paying bills)? `stress_moneyemplo`
- 7) Did you experience increased stress related to your personal health? `stress_pershealth`
- 8) Did you experience increased stress related to the health of your family members? `stress_healthfam`
- 9) Did you experience increased stress related to social anxiety: loneliness, lack of social interaction, lack of personal space, depression, lack of physical activity? `stress_anxiety`


- Preparing data for plotting
```{r 5.01, fig.height=7, fig.width=10, echo=FALSE}
#Selecting relevant columns, dropping NAs, and nonbinary gender respondents (because n = 3)
df.stress <- k.data %>% select(age:acad, stress_delaywork:stress_relation, stress_moneyemplo:stress_anxiety) %>% 
  drop_na() %>%
  filter(gender != "other_notsay")
#Calculating the percent of respondents with moderate, strong, or extreme stress (p.ss) for each topic
df.stress.all <- df.stress %>% group_by(gender) %>% summarize(
  p.ss.delaywork  = length(which(stress_delaywork %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_delaywork),
  p.ss.career     = length(which(stress_career %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_career),
  p.ss.burden     = length(which(stress_burden %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_burden),
  p.ss.relation   = length(which(stress_relation %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_relation),
  p.ss.moneyemplo = length(which(stress_moneyemplo %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_moneyemplo),
  p.ss.pershealth = length(which(stress_pershealth %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_pershealth),
  p.ss.healthfam  = length(which(stress_healthfam %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_healthfam),
  p.ss.anxiety    = length(which(stress_anxiety %in% 
                                  c("modstress", "strongstress", "extrastress")))/length(stress_anxiety), .groups = "drop") %>%
  melt(id.vars = "gender")
#Adding more presentable labels
df.stress.all <- df.stress.all %>% mutate(label = case_when(
  variable == "p.ss.delaywork"  ~ "Interruptions/delays at work",
  variable == "p.ss.career"     ~ "Future career plans",
  variable == "p.ss.burden"     ~ "Burden of household work",
  variable == "p.ss.relation"   ~ "Personal relationships",
  variable == "p.ss.moneyemplo" ~ "Money/financial responsibilities",
  variable == "p.ss.pershealth" ~ "Personal health",
  variable == "p.ss.healthfam"  ~ "Health of family members",
  variable == "p.ss.anxiety"    ~ "Anxiety or social stress"))

```

- Plotting
```{r 5.02, fig.height=7, fig.width=10, echo=FALSE}
#Putting all the thematic changes to the plot in a list:
MySpecial <- list(  
  # move the x axis labels up top
  scale_x_discrete(position = "top"),
  theme_bw(),
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none"),
  # Remove the panel border
  theme(panel.border     = element_blank()),
  # Remove just about everything from the y axis
  theme(axis.title.y     = element_blank()),
  theme(axis.text.y      = element_blank()),
  theme(panel.grid.major.y = element_blank()),
  theme(panel.grid.minor.y = element_blank()),
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()),
  theme(panel.grid.major.x = element_blank()),
  theme(axis.text.x.top      = element_text(size=12)),
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()),
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)),
  theme(plot.subtitle    = element_text(hjust = 0.5))
)


#Manually change the sample size in the subtitle
ggplot(data = df.stress.all, aes(x = gender, y = value, group = variable)) +
  geom_line(aes(color = variable, alpha = 1), size = 1) +
  geom_point(aes(color = variable, alpha = 1), size = 3) +
  geom_text_repel(data = df.stress.all %>% filter(gender == "female"), 
                  aes(label = paste0(label, " : ", round(value*100, 2), "%")) , 
                  hjust = "right", 
                  size = 4, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text_repel(data = df.stress.all %>% filter(gender == "male"), 
                  aes(label = paste0(round(value*100, 2), "%")) , 
                  hjust = "right", 
                  size = 4, 
                  nudge_x = .5, 
                  direction = "y") +
  MySpecial +
  labs(
    title    = "Percent of respondents reporting moderate or greater stress related to:",
    subtitle = "n = 770",
    caption  = "Madagascar STEM students and professionals"
  )

```


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 6 | Preliminary data visualizations: Household and contact patterns

</div>

***
***

- Selected questions from the survey:

  - 4.04 Not including bathrooms or kitchen, how many rooms does the house you live in have? `nb_room`

  - 4.06 Household members `hh_member_count` : `age_hh_member`, `age_hh_member_001`:`age_hh_member_014`

  - 5.02 In the last week, approximately with how many people besides those in your household did you spend more than 10 minutes in close contact with? `close_contact`

(Preparing the data for plotting)

```{r 6.01, fig.height=7, fig.width=10, echo=FALSE}
#Renaming the index column (to use for joining later)
df.hhc <- k.data %>% rename(index = "_index") %>% 
  #Selecting relevant columns
  select(index, age, gender, region, acad, 
         nb_room,
         hh_member_count,
         close_contact) %>%
  #Converting columns to numeric
  mutate(age = as.numeric(age), nb_room = as.numeric(nb_room), hh_member_count = as.numeric(hh_member_count)) %>%
  #Adding 1 to the hh size (to include the respondent + the other members of the household)
  mutate(hh_member_count = hh_member_count + 1) %>%
  #Calculating approximate age of the respondent and storing as age_hh_memb_i
  mutate(age_hh_memb_i = 2021-age) %>%
  #Using join to add the columns with ages of the other household members
  #Doing separately so can convert all columns to numeric using mutate_if()
  full_join(k.data %>% rename(index = "_index") %>% 
              #renaming the column with the age of the first other household member (the 2nd member of the household)
              # age_hh_memb_000
              mutate(age_hh_memb_000 = age_hh_memb) %>%
              select(index, age_hh_memb_000, age_hh_memb_001:age_hh_memb_014) %>% 
              mutate_if(is.character,as.numeric),
            by = "index") %>%
  #Subsetting to Antananarivo region Analamanga
  filter(region == "analamang") %>%
  #Removing illogical responses (e.g., 0 rooms in the house, negative number of hh members)
  #(e.g. hh_member count > 14 because didn't record ages for more than 14 individuals)
  filter(nb_room > 0) %>% filter(hh_member_count > 0) %>% filter(hh_member_count < 15) %>%
  #Calculating the number of people per room in houses
  mutate(pers_per_room = hh_member_count/nb_room) %>%
  #Determining which records have full household age data and removing incomplete records
  mutate(cols_w_age = 1 + rowSums(!is.na(select(., age_hh_memb_000:age_hh_memb_014))),
         hh_diff = hh_member_count - cols_w_age) %>%
  #Removing households that did not report the age of each member
  filter(hh_diff < 1) %>%
  #Calculating the age of eldest individual
  rowwise() %>% mutate(max_age = max(c(age_hh_memb_i, 
                                       age_hh_memb_000, age_hh_memb_001, age_hh_memb_002, age_hh_memb_003,
                                       age_hh_memb_004, age_hh_memb_005, age_hh_memb_006, age_hh_memb_006,
                                       age_hh_memb_007, age_hh_memb_008, age_hh_memb_009, age_hh_memb_010,
                                       age_hh_memb_011, age_hh_memb_012, age_hh_memb_013, age_hh_memb_014),
                                     na.rm = TRUE)) %>% ungroup() %>%
  #Ordering by household size and age of eldest
  arrange(hh_member_count, max_age) %>%
  #Giving a rank for plotting (index_hh) that restarts at 1 for each household size
  group_by(hh_member_count) %>% mutate(index_hh = 1:length(index)) %>% ungroup() %>%
  #Melting so each individual is on a row
  melt(id.vars = c("index", "index_hh", "age", "gender", "region", "acad", "nb_room", "hh_member_count", "close_contact",
                   "pers_per_room", "cols_w_age", "hh_diff", "max_age")) %>%
  #For plotting with a different color, adding a marker for individuals over 65
  mutate(old = as.factor(ifelse(max_age > 64, 1, 0))) %>%
  #Deleting rows with incomplete data
  drop_na()
```

(plotting the household size distribution)

```{r 6.02, fig.height=7, fig.width=10, echo=FALSE}
#Highlighting households with individuals over 65
df.hhc %>% ggplot(aes(x = value, y = index_hh, color = old)) +
  geom_point() +
  #Separating each household size
  facet_grid(~ hh_member_count, scales = "fixed") +
  xlab("Age of household members") + ylab("Household") +
  scale_color_manual(values=c("black", "#c51162")) +
  theme_bw() +
  scale_y_continuous(breaks = c(1:88)) +
  rremove("y.text") + rremove("legend")
```

(plotting the histogram of the number of individuals per room)

```{r 6.03, fig.height=7, fig.width=10, echo=FALSE}
#Keeping the pers_per_room from the melted df.hhc
df.hhc %>% group_by(index) %>% summarize(pers_per_room = max(pers_per_room), .groups = "drop") %>%
  ggplot(aes(x = pers_per_room)) +
  geom_histogram(binwidth=1, fill = "#00695c") + 
  xlab("Number of individuals per room in the house \n (excluding bathrooms and kitchen)") +
  ylab("Count") + theme_bw()
```



