---
title: "Weekly_Data_Processing"
author: "Benny Rice"
date: "2/8/2021"
output: html_document
---

```{r setup, include = FALSE, eval = TRUE, echo = TRUE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
```

***
***
<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

## HEADER INFO

- Benny Rice | Department of Ecology and Evolutionary Biology | Princeton University | b.rice@princeton.edu
- Code associated with processing data from the **Impacts of Covid-19 on Malagasy STEM** project
- Apologies in advance for amateurish code (ie all the loops and clunkiness)
- In colloboration with Lova Marline, Miary Raselimanana, Seheno Andriantsaralaza, Hervet Randriamady

</div>

***

(Set up: Loading necessary libraries)
```{r i1, echo = FALSE, message = FALSE, eval = TRUE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(reshape2)
library(ggpubr)
library(ggalt)
library(ggrepel)
library(here)
library(gridExtra)
library(readxl)
```

***
***

#### OUTLINE:

- Section 1:
- Section 2:
- Section 3:
- Section 4:
- Section 5:


**FIX** Update outline at the end (add figures and tables interspersed ^)


***
***

<style>
div.green { background-color:#d1ebd6; border-radius: 5px; padding: 10px;}
</style>
<div class = "green">

### Section 1 | Reading in data downloaded from Kobo Collect (xls form, English)

</div>

***
***

- Data is read from an xls file that is manually downloaded from the Kobo Collect account
  - Selecting export options:
    - Export type `XLS`
    - Value and header format `XML values and headers`
    - Do not select `Include fields from all 24 deployed versions`
  
  - Then uploaded to the GitHub repository for this project
- Data file name should include the data at which data was downloaded

```{r 1.01, eval = TRUE}
k.data <- read_xlsx(here(""))
```

